Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-14 GWLDCII.tex
read through section 2

In Section \ref{sec poles}, we show that the denominator $R(W)$ is determined by the positroid cell $\Sigma(W)$ and the structure of $W$, as encapsulated by $C(W)$. In fact, it can be read directly off of $C(W)$, in terms of a characterization of $\Sigma(W)$ called the Grassmann necklace (see Definition~\ref{def:grassmann necklace}). We also give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future. \todo{cite the theorems where these results appear}

@@

  Alternatively if we forget about the matroid and simply think about the condition of linear independence in the matrix $C(W)$, the corollary can also be proved directly by linear algebra and the definition of $C(W)$ as follows.

@@

Our first goal is therefore to find a better method of obtaining the positroid associated to a given Wilson loop diagram; this is the focus of the next section.

>>>>

In Section \ref{sec poles}, we show that the denominator $R(W)$ is determined by the positroid cell $\Sigma(W)$ and the structure of $W$, as encapsulated by $C(W)$. In fact, it can be read directly off of $C(W)$, in terms of a characterization of $\Sigma(W)$ called the Grassmann necklace (see Definition~\ref{def:grassmann necklace}) as shown in Algorithm \ref{alg:put GN on WLD}. We also give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.

@@

  Alternatively if we forget about the \st{matroid} {\color{violet} diagram} \sanote{okay?} and simply think about the condition of linear independence in the matrix $C(W)$, the corollary can also be proved directly by linear algebra and the definition of $C(W)$ as follows.

@@

Our first goal is therefore to find a better method of obtaining the positroid associated to a given Wilson loop diagram; this is the focus of the next section. \sanote{Should the 2 paras before the remark be moved to when whe walk about the GN algorithm?}
